\documentclass[11pt]{article}
\usepackage{amsfonts, amssymb, amsmath, hyperref}

\parindent 0px

\title{My \LaTeX\ Document}
\author{Amirhossein}
\date{\today}

\begin{document}
\tableofcontents
\maketitle


	This will produce \textit{italicized} text.
	
	This will produce \textbf{bold} text.

	This will produce \textsc{capitalize} text.
	
	This will produce \texttt{typewriter font} text.		
	
	Please visit EE of AUT : \url{https://ee.aut.ac.ir}
	
	\href{https://ee.aut.ac.ir}{EE of AUT Website}
	
	\vspace{2cm}
	
	Please excuse my dear aunt Sally.
	
	Please excuse my \begin{large} dear aunt Sally \end{large}.
	
	Please excuse my \begin{Large} dear aunt Sally \end{Large}.
	
	Please excuse my \begin{huge} dear aunt Sally \end{huge}.
	
	Please excuse my \begin{Huge} dear aunt Sally \end{Huge}.
	
	\vspace{1cm}
	
	Please excuse my \begin{normalsize} dear aunt Sally \end{normalsize}.
	
	Please excuse my \begin{small} dear aunt Sally \end{small}.
	
	Please excuse my \begin{scriptsize} dear aunt Sally \end{scriptsize}.
	
	Please excuse my \begin{tiny} dear aunt Sally \end{tiny}.
	
	\vspace{2cm}
	
	\begin{center}
		This line is centered.
	\end{center}
	
	\begin{flushright}
		This line is right-justified.
	\end{flushright}
	
	\begin{flushleft}
		This line is left-justified.
	\end{flushleft}
	
	
	\Large	
	hole document hole document hole document hole document hole document
	hole document hole document hole document \begin{normalsize}hole document\end{normalsize} hole document
	
	\normalsize
	
	
	\section{Linear Functions}
		\subsection{Slope-Intercept Form}
			\subsubsection{Example1:}
			\subsubsection{Example2:}
		\subsection{Standarad Form}
		\subsection{Pont-Slope Form}
	
	\section{Quadric Functions}
		\subsection{Vertex Form}
		\subsection{Standard Form}
		\subsection{Factored Form}
	
	
	
	
	
	

	
	
	
	
	
\end{document}